Cover letter for the original IJRR submission

### 2017-10-09 reviews_tro/reviewer_response.tex

\quot{* Finally, I would suggest providing explicit git SHAs or tags for all
of the github links. I've personally made the mistake of linking to a
github project in a paper, only to have that project change and
eventually delete the specific code I was citing. }
\as{The reviewer is absolutely right. We indeed encounter the issue with other researchers that are currently using our planner. 
To address this issue, the link for the code now points at a website, where instructions are given to install the correct version of the project, on a separate branch
dedicated to the installation of the planner.
Regarding the link to the python code for the OCP that addresses P3, we provided an explicit git SHAs, as suggested by the reviewer.}
\qt{(Section VII) Both HPP and our planner can be simply downloaded and compiled by following the instructions on
\url{https://humanoid-path-planner.github.io/hpp-doc/download.html?branch=rbprm}. \\
(Appendix C) To address the other scenarios, we propose a new implementation, entirely open source (\url{https://github.com/stonneau/python_sandbox/releases/tag/tro_paper} ), which can be integrated directly in our motion planner software. }
\done

\bigskip
We now join a diff file comparing the original and current submissions.
The text appearing in \textcolor{blue} denotes the additions. We used the latexdiff tools to generate this file, which is not fully compatible with the latex math package.
For this reason, errors appear in the document, in particular regarding the subsections number. However, we think that this diff file will help the reviewers locate precisely
where the modifications occured in the document. The reviewers will also notice that we reformulated the description our P3 solver in Appendix C, to better clarify what variables
are used, and what variables are implicit (that is computed from the others).

### 2017-10-09 body/appendix_optim.tex
typo in optim

\begin{equation} \label{eq:qp_rob} \begin{aligned}
%~ \find \quad & \mx{R} \in \Rv{3\times T}, \mxdd{C} \in  \Rv{6\times T} \\
%~ \minimize_{\mathbf{c}(t), \mathbf{\dot{c}}(t), \mathbf{\ddot{c}}(t), \mathbf{w}(t)}  \quad & \sum_{u=0}^{2} \int_{t_u}^{t_u + \Delta t_u}  \ell(\mathbf{c}(t), \mathbf{\dot{c}}(t), \mathbf{\ddot{c}}(t), \mathbf{w}(t)) \text{dt}  \\
\minimize_{\mathbf{\ddot{c}}(t), \dot{L}(t)}  \quad & \sum_{u=0}^{2} \int_{t_u}^{t_u + \Delta t_u}  \ell(\mathbf{\ddot{c}}(t), \dot{L}(t)) \text{dt}  \\
%~ \st \quad & \mathbf{\ddot{c}}(t) = dyn(\mathbf{c}(t), \mathbf{\dot{c}}(t), \mathbf{w}(t)) \\
%~ \st \quad & \mathbf{c}(t) =  dyn(\mathbf{\ddot{c}}, \mathbf{c}_{\mathbf{q}_0} )  \\
\st \quad & \mathbf{A}_u \mathbf{w}(t)  \leq \mathbf{b}_u , \forall t \in  \left[t_u, t_u + \Delta t_u \right[, \forall u \\
	\quad & \mathbf{Y}_u \mathbf{c}(t)  \leq \mathbf{y}_u , \forall t \in  \left[t_u, t_u + \Delta t_u \right[, \forall u \\
	\quad & \mathbf{c}(0)  = \mathbf{c}_{\mathbf{q}_0} \\
	\quad & \mathbf{c}(T)  = \mathbf{c}_{\mathbf{q}_1} \\
	\quad & \mathbf{c}(0)  = \mathbf{\dot{c}}(0)  = \mathbf{\ddot{c}}(0) = \mathbf{0}\\
	\quad & \mathbf{c}(T)  = \mathbf{\dot{c}}(T)  = \mathbf{\ddot{c}}(T) = \mathbf{0}\\
    %~ \quad & ({\vct{r}}\tra\vct{r}=1,  \forall t  ?) \\
    %~ \quad & \delta t \sum\limits_1^{T-1}{\vc{r}^1}\tra {\vc{r}^1} \ge t_{transit} \\
    %~ \quad & \mx{A}_{\int} \mxdd{C} \leq \vc{a}_{\int} \\
    %~ \quad & \mx{V}_{\int} \mxd{C} \leq \vc{v}_{\int} \\
    %~ \quad & \mx{B}_{\int}^{1} \mx{C} \leq \vc{b}_{\int} \\
    %~ \quad & [\vc{c}_0\tra, \vcd{c}_0\tra]\tra = \vc{x}_0 \\
    %~ \quad & \vc{c}_T = \vc{c}_T^{input} \\
\end{aligned} \end{equation}
%~ \adnote{Did you really use w as a variable of your problem? Or do you compute it inside your constraint function as a function of the CoM pos and acc? And what about dL? It appears in the definition of w but then it is no longer there in the problem definition!}
The cost function $\ell$ is a weighted sum of the angular momentum and center-of-mass acceleration variation over the whole trajectory.
The center-of-mass positions and velocities $\mathbf{c}(t)$, $\mathbf{\dot{c}}(t)$ are interval variables, obtained through the double integration of $\mathbf{\ddot{c}}(t)$.
Then $\mathbf{w}(t)$ is obtained directly from these variables. $\mathbf{c}_{\mathbf{q}_0}$ and $\mathbf{c}_{\mathbf{q}_1}$ are the center-of-mass positions for configurations
 $\mathbf{q}_0$ and $\mathbf{q}_1$ respectively.
%~ The system dynamics $dyn$ tie together the position, velocity and acceleration of the center of mass. 
$\mathbf{Y}_u$ and $\mathbf{y}_u$ denote stacked kinematic constraints on the center of mass position, determined by the active contact locations.
The inequalities for each contact are determined in the same way that the reachable workspace is computed in Appendix~\ref{app:rom}, with
the effector serving as root. % (a triangulated object is a polytope, and as such can be described as a set of linear inequalities).

>>>>

\begin{equation} \label{eq:qp_rob} \begin{aligned}
%~ \find \quad & \mx{R} \in \Rv{3\times T}, \mxdd{C} \in  \Rv{6\times T} \\
%~ \minimize_{\mathbf{c}(t), \mathbf{\dot{c}}(t), \mathbf{\ddot{c}}(t), \mathbf{w}(t)}  \quad & \sum_{u=0}^{2} \int_{t_u}^{t_u + \Delta t_u}  \ell(\mathbf{c}(t), \mathbf{\dot{c}}(t), \mathbf{\ddot{c}}(t), \mathbf{w}(t)) \text{dt}  \\
\minimize_{\mathbf{\ddot{c}}(t), \dot{L}(t)}  \quad & \sum_{u=0}^{2} \int_{t_u}^{t_u + \Delta t_u}  \ell(\mathbf{\ddot{c}}(t), \dot{L}(t)) \text{dt}  \\
%~ \st \quad & \mathbf{\ddot{c}}(t) = dyn(\mathbf{c}(t), \mathbf{\dot{c}}(t), \mathbf{w}(t)) \\
%~ \st \quad & \mathbf{c}(t) =  dyn(\mathbf{\ddot{c}}, \mathbf{c}_{\mathbf{q}_0} )  \\
\st \quad & \mathbf{A}_u \mathbf{w}(t)  \leq \mathbf{b}_u , \forall t \in  \left[t_u, t_u + \Delta t_u \right[, \forall u \\
	\quad & \mathbf{Y}_u \mathbf{c}(t)  \leq \mathbf{y}_u , \forall t \in  \left[t_u, t_u + \Delta t_u \right[, \forall u \\
	\quad & \mathbf{c}(0)  = \mathbf{c}_{\mathbf{q}_0} \\
	\quad & \mathbf{c}(T)  = \mathbf{c}_{\mathbf{q}_1} \\
	\quad & \mathbf{c}(0)  = \mathbf{\dot{c}}(0)  = \mathbf{\ddot{c}}(0) = \mathbf{0}\\
	\quad & \mathbf{c}(T)  = \mathbf{\dot{c}}(T)  = \mathbf{\ddot{c}}(T) = \mathbf{0}\\
    %~ \quad & ({\vct{r}}\tra\vct{r}=1,  \forall t  ?) \\
    %~ \quad & \delta t \sum\limits_1^{T-1}{\vc{r}^1}\tra {\vc{r}^1} \ge t_{transit} \\
    %~ \quad & \mx{A}_{\int} \mxdd{C} \leq \vc{a}_{\int} \\
    %~ \quad & \mx{V}_{\int} \mxd{C} \leq \vc{v}_{\int} \\
    %~ \quad & \mx{B}_{\int}^{1} \mx{C} \leq \vc{b}_{\int} \\
    %~ \quad & [\vc{c}_0\tra, \vcd{c}_0\tra]\tra = \vc{x}_0 \\
    %~ \quad & \vc{c}_T = \vc{c}_T^{input} \\
\end{aligned} \end{equation}
%~ \adnote{Did you really use w as a variable of your problem? Or do you compute it inside your constraint function as a function of the CoM pos and acc? And what about dL? It appears in the definition of w but then it is no longer there in the problem definition!}
The cost function $\ell$ is a weighted sum of the angular momentum and center-of-mass acceleration variation over the whole trajectory.
The center-of-mass positions and velocities $\mathbf{c}(t)$, $\mathbf{\dot{c}}(t)$ are internal variables, obtained through the double integration of $\mathbf{\ddot{c}}(t)$.
Then $\mathbf{w}(t)$ is obtained directly from these variables. $\mathbf{c}_{\mathbf{q}_0}$ and $\mathbf{c}_{\mathbf{q}_1}$ are the center-of-mass positions for configurations
 $\mathbf{q}_0$ and $\mathbf{q}_1$ respectively.
%~ The system dynamics $dyn$ tie together the position, velocity and acceleration of the center of mass. 
$\mathbf{Y}_u$ and $\mathbf{y}_u$ denote stacked kinematic constraints on the center of mass position, determined by the active contact locations.
The inequalities for each contact are determined in the same way that the reachable workspace is computed in Appendix~\ref{app:rom}, with
the effector serving as root. % (a triangulated object is a polytope, and as such can be described as a set of linear inequalities).
